Thermodynamic response functions in a cell fluid model

### 2024-09-15 paper_text.tex
add ISBN to the Johnston book on vdW fluids

	\bibitem{Johnston2014book} D.C.~Johnston.
	\textit{\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid.}} (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1]

>>>>

	\bibitem{Johnston2014book} D.C.~Johnston.
	\textit{\href{https://dx.doi.org/10.1088/978-1-627-05532-1}{Advances in Thermodynamics of the van der {W}aals Fluid.}} (Morgan \& Claypool Publishers, 2014) [doi: 10.1088/978-1-627-05532-1][ISBN: 978-1-627-05532-1]
